---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hwep

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CRAN status](https://www.r-pkg.org/badges/version/hwep)](https://CRAN.R-project.org/package=hwep)
[![R-CMD-check](https://github.com/dcgerard/hwep/workflows/R-CMD-check/badge.svg)](https://github.com/dcgerard/hwep/actions)
[![codecov](https://codecov.io/gh/dcgerard/hwep/branch/main/graph/badge.svg?token=X6QJRSQBXQ)](https://codecov.io/gh/dcgerard/hwep)
<!-- badges: end -->

Inference concerning equilibrium and random mating in autopolyploids. Methods are available to test for equilibrium and random mating at any even ploidy level (>2) in the presence of double reduction. For autopolyploid populations in equilibrium, methods are available to estimate the degree of double reduction. We also provide functions to calculate genotype frequencies at equilibrium, or after one or several rounds of random mating, given rates of double reduction.

The main functions for inference are:

- `hwefit()`: Fit either `hwelike()`,`rmlike()`, `hweustat()`, or 
  `hwenodr()` across many loci. Parallelization is supported through the 
  [future](https://cran.r-project.org/package=future) package.
  
- `hwelike()`: Likelihood inference for equilibrium.
  This function estimates the rate of double reduction given
  equilibrium, and tests for at most small deviations from
  equilibrium.
  
- `rmlike()`: Likelihood inference for random mating in polyploids. 
  This function tests for random mating and estimates gametic frequencies 
  given random mating. This function does not assume a model for meiosis.
  
- `hweustat()`: U-statistic approach for equilibrium and double reduction. 
   This function tests for equilibrium given double reduction rates and 
   estimates these rates given equilibrium.
   
- `hwenodr()`: Implements a likelihood ratio test that tests for Hardy-Weinberg equilibrium in autopolyploids given no double reduction.

Functions are provided for calculating genotype frequencies for individuals and gametes:

- `gsegmat()`: Produces the segregation probabilities for gamete dosages given parental dosages and the double reduction rate.

- `gsegmat_symb()`: Provides a symbolic representation of the output of `gsegmat()`.

- `zsegarray()`: Obtains offspring genotype probabilities given parental probabilities, the ploidy of the species, and the overdispersion parameter, for all possible parental genotypes.

- `freqnext()`: Updates the genotype frequencies after one generation of random mating.

- `hwefreq()`: Calculate genotype frequencies at equilibrium.

The bounds on the double reduction rate under the complete equational segregation model are provided by `drbounds()`.

## Installation

<!-- You can install the released version of hwep from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ```{r, eval = FALSE} -->
<!-- install.packages("hwep") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/dcgerard/hwep) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("dcgerard/hwep")
```

## Citation

To cite hwep in publications use:

> Gerard D (2021). "Double reduction estimation and equilibrium tests in natural autopolyploid populations." _Unpublished Manuscript_.

A BibTeX entry for LaTeX users is

``` tex
@Article{,
  title = {Double reduction estimation and equilibrium tests in natural autopolyploid populations},
  author = {David Gerard},
  journal = {Unpublished Manuscript},
  year = {2021},
}
```

## Code of Conduct

Please note that the hwep project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
