---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hwep

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CRAN status](https://www.r-pkg.org/badges/version/hwep)](https://CRAN.R-project.org/package=hwep)
[![R-CMD-check](https://github.com/dcgerard/hwep/workflows/R-CMD-check/badge.svg)](https://github.com/dcgerard/hwep/actions)
[![codecov](https://codecov.io/gh/dcgerard/hwep/branch/main/graph/badge.svg?token=X6QJRSQBXQ)](https://codecov.io/gh/dcgerard/hwep)
<!-- badges: end -->

Inference concerning Hardy-Weinberg equilibrium (HWE) in polyploids. Methods are available to test for HWE at any ploidy level in the presence of double reduction. For autopolyploid populations in HWE, methods are available to estimate the degree of double reduction. We also provide functions to calculate genotype frequencies at equilibrium given rates of double reduction.

The main functions are:

- `hwefit()`: Fit either `hwetetra()`,`rmlike()`, or `hwemom()` across many 
  loci. Parallelization is supported through the 
  [future](https://cran.r-project.org/package=future) package.
- `hwetetra()`: Likelihood inference for tetraploids. Includes tests for 
  random mating, only small deviations from HWE, and the presence
  of double reduction.
- `rmlike()`: Likelihood inference for random mating in polyploids. 
  This function tests for random mating and estimates gametic frequencies 
  given random mating. This function does not assume a model for meiosis.
- `hweustat()`: U-statistic approach for equilibrium and double reduction. 
   This function tests for equilibrium given double reduction rates and 
   estimates these rates given equilibrium.
- `hwenodr()`: Implements a likelihood ratio test that tests for HWE in
  autopolyploids given no double reduction.

## Installation

You can install the released version of hwep from [CRAN](https://CRAN.R-project.org) with:

```{r, eval = FALSE}
install.packages("hwep")
```

You can install the development version from [GitHub](https://github.com/dcgerard/hwep) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("dcgerard/hwep")
```

## Citation

To cite hwep in publications use:

> Gerard D (2021). "Double reduction estimation and equilibrium tests in natural autopolyploid populations." _Unpublished Manuscript_.

A BibTeX entry for LaTeX users is

``` tex
@Article{,
  title = {Double reduction estimation and equilibrium tests in natural autopolyploid populations},
  author = {David Gerard},
  journal = {Unpublished Manuscript},
  year = {2021},
}
```

## Code of Conduct

Please note that the hwep project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
