---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hwep

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CRAN status](https://www.r-pkg.org/badges/version/hwep)](https://CRAN.R-project.org/package=hwep)
[![R-CMD-check](https://github.com/dcgerard/hwep/workflows/R-CMD-check/badge.svg)](https://github.com/dcgerard/hwep/actions)
[![codecov](https://codecov.io/gh/dcgerard/hwep/branch/main/graph/badge.svg?token=X6QJRSQBXQ)](https://codecov.io/gh/dcgerard/hwep)
<!-- badges: end -->

Inference concerning Hardy-Weinberg equilibrium (HWE) in polyploids. Methods are available to test for HWE at any ploidy level in the presence of double reduction. For autopolyploid populations in HWE, methods are available to estimate the degree of double reduction. We also provide functions to calculate genotype frequencies at equilibrium given rates of double reduction.

## Installation

You can install the released version of hwep from [CRAN](https://CRAN.R-project.org) with:

```{r, eval = FALSE}
install.packages("hwep")
```

You can install the development version from GitHub with:
```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("dcgerard/hwep")
```

## Code of Conduct

Please note that the hwep project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
